### 2015-03-02 fundamentals/impl.tex
Well-written, but unnecessary platitude about documentation being deleted for brevity
Again, for brevity

All of the public interface (the \gls{API}) must be documented as required by the \Cyclus
\gls{QA} policy. This certifies that the intended goals of an \gls{API} are communicated
explicity by the author in prose form. Future developers are then able to
compare the implementation versus the documentation to discern whether or not
these are in agreement. Documentation is thus a secondary higher-level information
stream.  In \Cyclus, this information is aggregated together into static
websites with the Doxygen \cite{van_heesch_doxygen:_2008} and Sphinx
\cite{brandl_sphinx_2014}
tools, and can be accessed at \url{http://fuelcycle.org}.

>>>>

All of the public interface (the \gls{API}) must be documented as required by
the \Cyclus \gls{QA} policy. This certifies that the intended goals of an
\gls{API} are communicated explicity by the author in prose form.  In \Cyclus,
this information is aggregated together into static websites with the Doxygen
\cite{van_heesch_doxygen:_2008} and Sphinx \cite{brandl_sphinx_2014} tools, and
can be accessed at \url{http://fuelcycle.org}.
